Pillar 2 - Topic Modeling

### 2019-03-11 Pillar 2 - Topic Modeling.Rmd
applies get gamma and get betta before saving

>>>>

```{r getting gamma and beta, eval = TRUE}
get_beta <- function(results){

  tidy(results, matrix = "beta")           %>%
    mutate(topic = paste("Topic", topic) ) %>%
      arrange(topic, desc(beta) )

get_gamma <- function(results){

  tidy(results, matrix = "gamma")          %>%
    mutate(topic = paste("Topic", topic) ) %>%
      arrange(topic, desc(gamma) )
}

```{r applying get_gamma and get_beta, eval = TRUE}
topic_model_gb <- topic_model %>%
  transmute(
    n_topic    = n_topic,
    g_overview = TM_overview %>% map( .f = get_gamma),
    g_manual   = TM_manual   %>% map( .f = get_gamma),
    b_overview = TM_overview %>% map( .f = get_beta),
    b_manual   = TM_manual   %>% map( .f = get_beta)
      )
```

```{r saving tidy models, eval= TRUE}
save(topic_model_gb,
     file = "Output/topic_model_gb.RDATA")

save(topic_model_gb,
     file = "App/Recommender System/topic_model_gb.RDATA")
```
